---
title: "Turbidity"
author: "SS"
date: "November 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#This reads in the Reef Check data file and the mean global turbidity raster. It extracts the kd490 value for each Reef Check survey, and writes a csv 'Reef_Check_with_turbidity_kd490.csv'.

```{r load libraries}
library(ncdf4)
library(stringr)
```

#set path for where you keep the bleaching data
Bleaching_data_directory="C:/Users/Shannon/Desktop/Ecoregions/turbidity/Final"
#set path for the external hard drive where you have downloaded the CoRTAD data
turbidity_directory="D:/Lab Data/Global/Kd490/Monthly/4km/MODIS_Aqua/netcdf"

#read in the Reef Check csv
Bleaching_Data <- read.csv(file="Reef_Check_with_Cortad_variables_with_annual_rate_of_SST_change.csv", header=TRUE, sep=",")
#use just the "Bleaching (% of population)" data, not the "Bleaching (% of colony)" data
Bleaching_Data=subset(Bleaching_Data, Organism.Code=="Bleaching (% of population)")

#2002_07 through 2017_02
setwd(turbidity_directory)
#first just read in one of the months so we can do some calculations
turbidity<-nc_open("MODIS_Aqua_Monthly_4km_KD490_2002_07.nc", write=FALSE, readunlim=TRUE, verbose=FALSE)

#turbidity$var$Kd_490$units # "m^-1"

number_of_surveys<-dim(Bleaching_Data)[1]
```{r calculate latitude grid cell}
turbidity$var$Kd_490$dim[[2]] #name "lat" $units "degree_north" len=4320
turbidity$var$Kd_490$dim[[2]]$vals

lat_step<-turbidity$var$Kd_490$dim[[2]]$vals[1]-turbidity$var$Kd_490$dim[[2]]$vals[2]

Bleaching_turbidity_lat_cell<-array(0, dim=number_of_surveys)

for (i in 1:number_of_surveys)
{
lat_grid_cell<-NA

if(is.na(Bleaching_Data$Latitude.Degrees[i]))
{lat_grid_cell<-NA}else{
n_lat_steps<-floor((turbidity$var$Kd_490$dim[[2]]$vals[1]-Bleaching_Data$Latitude.Degrees[i])/lat_step+1)

  if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]+lat_step)>=Bleaching_Data$Latitude.Degrees[i])
  {
    if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]-lat_step)<=Bleaching_Data$Latitude.Degrees[i])
    {lat_grid_cell<-n_lat_steps}
    else
    {
      repeat{
        n_lat_steps=n_lat_steps+1
        if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]-lat_step)<=Bleaching_Data$Latitude.Degrees[i]){
          if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]+lat_step)>=Bleaching_Data$Latitude.Degrees[i])
          {break}
        }
      }
      lat_grid_cell<-n_lat_steps
    }
    
  }
  
  if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]+lat_step)<Bleaching_Data$Latitude.Degrees[i])
  {
  repeat{
      n_lat_steps=n_lat_steps-1
      if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]+lat_step)>=Bleaching_Data$Latitude.Degrees[i])
      {
        if((turbidity$var$Kd_490$dim[[2]]$vals[n_lat_steps]-lat_step)<=Bleaching_Data$Latitude.Degrees[i])
        {break}
      }
    }
    lat_grid_cell<-n_lat_steps
  }
}
  Bleaching_turbidity_lat_cell[i]<-lat_grid_cell
}
```

```{r calculate longitude grid cell}
turbidity$var$Kd_490$dim[1] # $name "lon" $units "degree_east" len=8640
turbidity$var$Kd_490$dim[[1]]$vals

lon_step<-turbidity$var$Kd_490$dim[[1]]$vals[2]-turbidity$var$Kd_490$dim[[1]]$vals[1]

Bleaching_turbidity_lon_cell<-array(0, dim=number_of_surveys)

for (i in 1:length(Bleaching_Data$Longitude.Degrees))
{
lon_grid_cell<-NA

if(is.na(Bleaching_Data$Longitude.Degrees[i]))
{lon_grid_cell<-NA}else{
n_lon_steps<-floor(-1*(turbidity$var$Kd_490$dim[[1]]$vals[1]-Bleaching_Data$Longitude.Degrees[i])/lon_step+1)

  if(n_lon_steps>(length(turbidity$var$Kd_490$dim[[1]]$vals))){n_lon_steps<-(length(turbidity$var$Kd_490$dim[[1]]$vals))}
  if(n_lon_steps<1){n_lon_steps<-1}

  if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])+lon_step>=Bleaching_Data$Longitude.Degrees[i])
  {
    if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])-lon_step<Bleaching_Data$Longitude.Degrees[i])
    {lon_grid_cell<-n_lon_steps}
    else
    {
      repeat{
        n_lon_steps=n_lon_steps-1
        if(n_lon_steps>(length(turbidity$var$Kd_490$dim[[1]]$vals))){n_lon_steps<-length(turbidity$var$Kd_490$dim[[1]]$vals); break}
        if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])+lon_step>=Bleaching_Data$Longitude.Degrees[i]){
          if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])-lon_step<Bleaching_Data$Longitude.Degrees[i])
          {break}
        }
      }
      lon_grid_cell<-n_lon_steps
    }
    
  }
  
  if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])+lon_step<Bleaching_Data$Longitude.Degrees[i])
  {
  repeat{
      n_lon_steps=n_lon_steps+1
      if(n_lon_steps==0){n_lon_steps<-1; break}
      if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])-lon_step<=Bleaching_Data$Longitude.Degrees[i])
      {
        if((turbidity$var$Kd_490$dim[[1]]$vals[n_lon_steps])+lon_step>Bleaching_Data$Longitude.Degrees[i])
        {break}
      }
    }
    lon_grid_cell<-n_lon_steps
  }
}
  Bleaching_turbidity_lon_cell[i]<-lon_grid_cell
}

```

Bleaching_Data$kd490_value<-NA
setwd(turbidity_directory)
```{r kd490}
for (i in 1:dim(Bleaching_Data)[1]){
  yr<-as.character(Bleaching_Data$Year[i])
  date_string<-str_split(Bleaching_Data$Date[i], "-")
  month_string<-date_string[[1]][2]
  if (month_string=="Jan"){month<-"01"}
  if (month_string=="Feb"){month<-"02"}
  if (month_string=="Mar"){month<-"03"}
  if (month_string=="Apr"){month<-"04"}
  if (month_string=="May"){month<-"05"}
  if (month_string=="Jun"){month<-"06"}
  if (month_string=="Jul"){month<-"07"}
  if (month_string=="Aug"){month<-"08"}
  if (month_string=="Sep"){month<-"09"}
  if (month_string=="Oct"){month<-"10"}
  if (month_string=="Nov"){month<-"11"}
  if (month_string=="Dec"){month<-"12"}
  
  yr_month<-Bleaching_Data$Year[i]+(as.numeric(month)-1)/12
  if(yr_month>=2002.5 & yr_month<=2017.99){
    file_name<-paste("MODIS_Aqua_Monthly_4km_KD490_", yr, "_", month, ".nc", sep="")
    turbidity<-nc_open(file_name, write=FALSE, readunlim=TRUE, verbose=FALSE)
    turbidity_kd490<-ncvar_get(turbidity, varid="Kd_490")
    Bleaching_Data$kd490_value[i]<-turbidity_kd490[Bleaching_turbidity_lon_cell[i], Bleaching_turbidity_lat_cell[i]]
    Sys.sleep(0.2)
    if(is.na(Bleaching_Data$kd490_value[i])){
      expand=1
      Bleaching_Data$kd490_value[i]<-mean(na.omit(as.numeric(turbidity_kd490[max(Bleaching_turbidity_lon_cell[i]-expand, 1):min(Bleaching_turbidity_lon_cell[i]+expand,dim(turbidity_kd490)[2]), max(Bleaching_turbidity_lat_cell[i]-expand,0):min(Bleaching_turbidity_lat_cell[i]+expand,max(dim(turbidity_kd490)[1]))])))
      if(is.na(Bleaching_Data$kd490_value[i])){
        expand=2
        Bleaching_Data$kd490_value[i]<-mean(na.omit(as.numeric(turbidity_kd490[max(Bleaching_turbidity_lon_cell[i]-expand, 1):min(Bleaching_turbidity_lon_cell[i]+expand,dim(turbidity_kd490)[2]), max(Bleaching_turbidity_lat_cell[i]-expand,0):min(Bleaching_turbidity_lat_cell[i]+expand,max(dim(turbidity_kd490)[1]))])))
      } #close second if is.na turbidity value
    } #close first if is.na turbidity value
    print(i)
    nc_close(turbidity)
  } #close if bleaching yr month
} #close main for loop
```

write.csv(Bleaching_Data, file = file.path(home,'Reef_Check_with_turbidity_kd490.csv'),row.names=T)