---
title: "ordinal_regression_final"
author: "SS"
date: "November 24, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#This reads in a csv file containing Reef Check data along with the SST and turbidity data. It runs the data through an ordinal regression model. 

```{r initialization}
library(ggplot2)
library(R2jags)
```
home<-"C:/Users/Shannon/Desktop/Ecoregions/turbidity/Final"

ECO <- readOGR(file.path(home,'ecoregion_exportPolygon','ecoregion_exportPolygon.shp')) # ecoregions

```{r get rid of the holes in the polygon shapefiles}
ecos_list<-c()
for (i in 1:150){
  eco_i<-Polygons((Filter(function(f){f@ringDir==1}, ECO@polygons[[i]]@Polygons)), ID=i)
  ecos_list<-append(ecos_list, values=eco_i, after = length(ecos_list))
  Sys.sleep(.2)
}
ecos<-SpatialPolygons(ecos_list)

ecos$ERG<-ECO$ERG
ecos$Ecoregion<-ECO$Ecoregion
ecos@proj4string<-ECO@proj4string
ecos@plotOrder<-ECO@plotOrder
ecos@data<-ECO@data

ECO<-ecos
```

```{r read in and format data}
data <- read.csv(file=file.path(home,"Reef_Check_with_turbidity_kd490.csv"), header=TRUE, sep=",")
data <- subset(data, Organism.Code=="Bleaching (% of population)")
names(data)[names(data)=="ï..Reef.ID"]<-"Reef.ID"

source(file=file.path(home,"MyBUGSOutput.R"))

# calculate bleaching metrics
data$bleach.prez <- 0
data$bleach.prez[rowSums(data[c('S1','S2','S3','S4')],na.rm=T) >= 1] <- 1
data$avg.bleach <- rowSums(data[c('S1','S2','S3','S4')],na.rm=T)/rowSums(!is.na(data[c('S1','S2','S3','S4')]))
data$avg.bleach[data$avg.bleach < 1] <-0

# temperature
data$Temperature_Kelvin <- data$Temperature_Kelvin - 273.15
data <- data[!is.na(data$Temperature_Kelvin),]
data <- data[!is.na(data$kd490_value),]
data <-data[data$kd490_value<=1,]

```

```{r define severity level categories}
#4 categories for bleaching: none, mild, moderate, severe
data$severity<-"none"
data$severity[data$avg.bleach>=1 & data$avg.bleach<=10]<-"mild"
data$severity[data$avg.bleach>10 & data$avg.bleach<50]<-"moderate"
data$severity[data$avg.bleach>=50]<-"severe"
data$severity<-as.factor(data$severity)
```

data<-data[!is.na(data$Region),]
data<-data[!is.na(data$kd490_value),]

#Ordinal Regression. ranked scoring. ranging from 1="none" to 4="severe"
data$severity_score<-as.character(data$severity)
data$severity_score[data$severity=="none"]<-1
data$severity_score[data$severity=="mild"]<-2
data$severity_score[data$severity=="moderate"]<-3
data$severity_score[data$severity=="severe"]<-4
data$severity_score<-as.numeric(data$severity_score)
data$severity_score<-as.factor(data$severity_score)

names(data)[names(data)=="Region.x"]<-"Region"
data$ERG<-data$Region

data<-subset(data, select=c('kd490_value', 'Temperature_Kelvin', 'ERG', 'severity_score', 'Reef.ID'))

data$Reef.ID <- as.factor(as.character(data$Reef.ID))
sites_and_region_df <- data %>% distinct(Reef.ID, ERG) %>% ungroup()
sites_and_region_df$site <- as.factor(as.numeric(as.factor(sites_and_region_df$Reef.ID)))
sites_and_region_df$region <- as.factor(as.numeric(as.factor(as.character(sites_and_region_df$ERG))))
data <- left_join(data,sites_and_region_df,by='Reef.ID')
data$region<-as.factor(as.numeric(data$region))
data$site<-as.factor(as.numeric(data$site))


```{r only sst and turbidity and interaction}
X_raw <- data[c('kd490_value','Temperature_Kelvin')]
X_raw$turbidity_sst_interaction<-X_raw$kd490_value*X_raw$Temperature_Kelvin

standardize_function<-function(x){
  x.standardized=(x-mean(na.omit(x)))/sd(na.omit(x))
  return(x.standardized)
}

X_standardized <- X_raw; for(i in 1:ncol(X_raw)) X_standardized[,i] <- standardize_function(X_raw[,i])

X <- model.matrix(~ X_standardized$kd490_value  +  X_standardized$Temperature_Kelvin  +  X_standardized$turbidity_sst_interaction)

parameter_names<-c('Turbidity', 'SST', 'Turbidity_SST_interaction')
```

K <- length(levels(data$severity_score))
num_vars <- ncol(X)
win.data <- list(Y = data$severity_score,
                 num_surveys = nrow(data),
                 X = X,
                 K = K,
                 num_vars = num_vars,
                 Site = data$site, #Random effects identification 
                 R    = length(unique(data$region)),
                 J    = length(unique(data$site)),
                 region_for_each_site = sites_and_region_df$region
)

sink("ordinal_regression.txt")
cat("
    model{
    #PRIORS
    for (i in 1:num_vars) { beta[i]  ~ dnorm(0, 0.001) }

    #Prior for tau_Site
    sigma_Site ~ dgamma(0.001, 0.001)
    tau_site <- 1 / (sigma_Site * sigma_Site)
    
    #Prior for tau_ecoregion
    sigma_ecoregion ~ dgamma(0.001, 0.001)
    tau_ecoregion <- 1 / (sigma_ecoregion * sigma_ecoregion)
    
    # Hierarchical effects
    for(j in 1:J){ # J is total number of sites
    a[j] ~ dnorm(ecoregion[region_for_each_site[j]],tau_site) # each site is drawn from each ecoregion
    }
    
    for(z in 1:R){ # R is total number of ecoregions
    ecoregion[z] ~ dnorm(g[z],tau_ecoregion) # each ecoregion mean is drawn from a distribution with a global mean
    g[z] <- mu_global
    }
    mu_global ~ dnorm(0, 0.001) # prior for global mean

for (i in 1:num_surveys){
  Y[i] ~ dcat(p[i,])
  p[i,1] <-1-Q[i,1]
  for (r in 2:(K-1)){
    p[i,r] <- Q[i,r-1] - Q[i,r]
  }
  p[i,K] <-Q[i,(K-1)]
  for (r in 1:(K-1)){
    logit(Q[i,r]) <-inprod(beta[], X[i,]) - c[r] + a[Site[i]]
  }

#Simulated data, taken from the fitted model.
YNew[i] ~  dcat(p[i,])

loglik[i] <- logdensity.cat(Y[i], p[i,])
}

for (i in 1:(K-1)){dc[i] ~ dunif(0,100)}
c[1] <-dc[1]
for (i in 2:(K-1)){
  c[i] <-c[i-1] + dc[i]
}
    }
    ",fill = TRUE)
sink()

inits  <- function () {list(beta = rnorm(ncol(X), 0, 0.1), sigma_Site = runif(1, 0, 1), sigma_ecoregion = runif(1, 0, 1), mu_global = rnorm(1,0,1))}

params <- c("beta", "YNew")

G1 <- jags(data       = win.data,
           inits      = inits,
           parameters = params,
           model      = "ordinal_regression.txt",
           n.thin     = 1,
           n.chains   = 3,
           n.burnin   = 4000,
           n.iter     = 5000)

Y_New<-G1$BUGSoutput$mean$YNew

vars <- c("beta[2]","beta[3]","beta[4]")
OUT1 <- MyBUGSOutput(G1$BUGSoutput, vars)
print(OUT1, digits =3)

# coef plot
G1_df=data.frame(variableG1=parameter_names, MeanG1=OUT1[,1], Down=OUT1[,3], Up=OUT1[,4], Down_quarter=OUT1[,5], Up_quarter=OUT1[,6])
G1_df$color <- ("white")
G1_df$color[(G1_df$MeanG1 > 0) & (G1_df$Down>0)] <- 'red'
G1_df$color[(G1_df$MeanG1 < 0) & (G1_df$Up<0)] <- 'blue'

tiff(file=file.path(home,'Figure2.tif'),height=2000,width=2700,res=300)
ggplot(G1_df,aes(x=reorder(variableG1, MeanG1), MeanG1)) +
  geom_errorbar(aes(ymax=G1_df$Up, ymin=G1_df$Down), width=0) +
  geom_errorbar(aes(ymax=G1_df$Up_quarter, ymin=G1_df$Down_quarter), width=0, size=1.3) +
  geom_point(pch=21, size=4, fill=G1_df$color, color="black") +
  coord_flip(ylim=c(-3.2,3.2)) +
  scale_y_continuous(breaks=c(-3,-2,-1,0,1,2,3))+
  #theme_grey(base_size=15) +
  theme(axis.text.y = element_text(size=20, color="black"), axis.text.x = element_text(size=20, color="black"), text=element_text(size=24)) +
  theme(panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid"))+
  theme(panel.background = element_blank()) +
  guides(colour=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color="gray") +
  labs(y=expression(paste("Estimated ",gamma," coefficients")), x="")
dev.off()

write.csv(G1_df, file = file.path(home,'ordinal_coeffs_sst_turbidity_and_interaction.csv'),row.names=T)