---
title: "gamma_plots"
author: "SS"
date: "November 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#This reads in the Reef Check with kd490 (turbidity) data, determines probability densities of kd490 values for each bleaching severity level, and determines the mean kd490 value for each bleaching severity level. It creates the image file 'gamma_distribution_of_kd490_values_for_bleaching_levels_20191121.tif'. It determines goodness-of-fit. It determines the Kd490 value when the probability density of none_to_mild_bleaching becomes greater than the probability density of moderate_to_severe_bleaching.

#read in data
home<-"C:/Users/Shannon/Desktop/Ecoregions/turbidity/Final"
data <- read.csv(file=file.path(home,"Reef_Check_with_turbidity_kd490.csv"), header=TRUE, sep=",")
data <- subset(data, Organism.Code=="Bleaching (% of population)")
data$Lat <- data$Latitude.Degrees; data$Long <- data$Longitude.Degrees
names(data)[names(data)=="ï..Reef.ID"]<-"Reef.ID"

# calculate average bleaching
data$bleach.prez <- 0
data$bleach.prez[rowSums(data[c('S1','S2','S3','S4')],na.rm=T) >= 1] <- 1
data$avg.bleach <- rowSums(data[c('S1','S2','S3','S4')],na.rm=T)/rowSums(!is.na(data[c('S1','S2','S3','S4')]))
data$avg.bleach[data$avg.bleach < 1] <-0

```{r remove rows with NA}
data <- data[!is.na(data$Diversity),]
data <- data[!is.na(data$Latitude.Degrees),]
data <- data[!is.na(data$ClimSST),]
data <- data[!is.na(data$TSA_Frequency_Standard_Deviation),]
data <- data[!is.na(data$TSA_Frequency),]
data <- data[!is.na(data$Temperature_Kelvin),]
#data <- data[!is.na(data$Rate_of_SST_change),]
data <- data[!is.na(data$rate_of_SST_change),]
data <- data[!is.na(data$SSTA_DHW),]
data <- data[!is.na(data$SSTA_Frequency),]
data <- data[!is.na(data$Year),]
data <- data[!is.na(data$SSTA_Maximum),]
data <- data[!is.na(data$SSTA_Minimum),]
data <- data[!is.na(data$Depth),]
data <- data[!is.na(data$Temperature_Maximum),]
data <- data[!is.na(data$SSTA),]
data <- data[!is.na(data$TSA_DHW_Standard_Deviation),]
data <- data[!is.na(data$SSTA_Frequency_Standard_Deviation),]
data <- data[!is.na(data$Temperature_Kelvin_Standard_Deviation),]
#data <- data[!is.na(data$PAR_value),]
#data <- data[!is.na(data$kd490_value),]
```

```{r calculations}
turbidity_distribution <- fitdistr(na.omit(data$kd490_value),'gamma')
turbidity_distribution_for_bleaching <- fitdistr(na.omit(data$kd490_value[data$avg.bleach>0]),'gamma')
turbidity_distribution_with_no_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach==0]),'gamma')
turbidity_distribution_mild_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach>=1 & data$avg.bleach<=10]),'gamma')
turbidity_distribution_moderate_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach>10 & data$avg.bleach<50]),'gamma')
turbidity_distribution_severe_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach>=50]),'gamma')
x=seq(0,1,.001) 
y_no_bleaching=dgamma(x,as.numeric(turbidity_distribution_with_no_bleaching$estimate['shape']),as.numeric(turbidity_distribution_with_no_bleaching$estimate['rate']))
y_mild_bleaching=dgamma(x,as.numeric(turbidity_distribution_mild_bleaching$estimate['shape']),as.numeric(turbidity_distribution_mild_bleaching$estimate['rate']))
y_moderate_bleaching=dgamma(x,as.numeric(turbidity_distribution_moderate_bleaching$estimate['shape']),as.numeric(turbidity_distribution_moderate_bleaching$estimate['rate']))
y_severe_bleaching=dgamma(x,as.numeric(turbidity_distribution_severe_bleaching$estimate['shape']),as.numeric(turbidity_distribution_severe_bleaching$estimate['rate']))
lines(x, y_no_bleaching/sum(y_no_bleaching), col="blue", lwd=2)
lines(x, y_mild_bleaching/sum(y_mild_bleaching), col="orange", lwd=2)
lines(x, y_moderate_bleaching/sum(y_moderate_bleaching), col="red", lwd=2)
lines(x, y_severe_bleaching/sum(y_severe_bleaching), col="black", lwd=2)

mean_no_bleaching<-mean(na.omit(data$kd490_value[data$avg.bleach<1])) #0.06468577
mean_mild_bleaching<-mean(na.omit(data$kd490_value[data$avg.bleach>=1 & data$avg.bleach<=10])) #0.06095361
mean_moderate_bleaching<-mean(na.omit(data$kd490_value[data$avg.bleach>=10 & data$avg.bleach<=50])) #0.05647368
mean_severe_bleaching<-mean(na.omit(data$kd490_value[data$avg.bleach>=50])) #0.05070975
```

```{r gamma plot}
tiff(file=file.path(home,'Figure3.tif'),height=1000,width=2000,res=300)
x=seq(0,1,.001) 
plot(x, y_no_bleaching/sum(y_no_bleaching), col="blue", type="l",lwd=2, xlim=c(0,.3), ylim=c(0,.02), xlab=expression("K"[d]*"490"), ylab="Probability density")
lines(x, y_mild_bleaching/sum(y_mild_bleaching), col="orange", lwd=2)
lines(x, y_moderate_bleaching/sum(y_moderate_bleaching), col="red", lwd=2)
lines(x, y_severe_bleaching/sum(y_severe_bleaching), col="black", lwd=2)
abline(v=mean_no_bleaching, col="blue", lwd=1, lty=2, ylim=c(-1,1))
abline(v=mean_mild_bleaching, col="orange", lwd=1, lty=2)
abline(v=mean_moderate_bleaching, col="red", lwd=1, lty=2)
abline(v=mean_severe_bleaching, col="black", lwd=1, lty=2)
legend("topright", legend=c("None", "Mild (1-10%)", "Moderate (>10-50%)", "Severe (>50%)"), col=c("blue", "orange", "red", "black"),pch=NA, lty=1, lwd=2)
dev.off()
```

logLik(turbidity_distribution)  #16780.41 (df=2)
logLik(turbidity_distribution_for_bleaching) #4485.148 (df=2)
logLik(turbidity_distribution_with_no_bleaching) #12351.72 (df=2)
logLik(turbidity_distribution_mild_bleaching) #3361.311 (df=2)
logLik(turbidity_distribution_moderate_bleaching) #875.771 (df=2)
logLik(turbidity_distribution_severe_bleaching) #261.8319 (df=2)

#-2*ln((likelihood of null model)/(likelihood of alternative model))
logLik_pooled <- turbidity_distribution$loglik
#16780.41

#for no bleaching vs bleaching
logLik_sum <- turbidity_distribution_with_no_bleaching$loglik + turbidity_distribution_for_bleaching$loglik
LR<- (2)*(logLik_sum-logLik_pooled)  #112.9129
pchisq(2*(logLik_sum-logLik_pooled),df=2,lower.tail=FALSE) #<0.0001

```{r examine turbidity values (x) when one none_and_mild_bleaching probability density becomes greater than moderate_and_severe_bleaching probability density, and LR}
#for none_and_mild_bleaching vs moderate_and_severe_bleaching
turbidity_distribution_none_to_mild_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach<=10]),'gamma')
turbidity_distribution_moderate_to_severe_bleaching<-fitdistr(na.omit(data$kd490_value[data$avg.bleach>10]),'gamma')
logLik_sum <- turbidity_distribution_none_to_mild_bleaching$loglik + turbidity_distribution_moderate_to_severe_bleaching$loglik
LR<- (2)*(logLik_sum-logLik_pooled)  #49.1311
pchisq(2*(logLik_sum-logLik_pooled),df=2,lower.tail=FALSE) #<0.0001


#closely examine where the probability density for none_to_mild_bleaching becomes greater than the probability density for moderate_to_severe_bleaching 
x_testing<-seq(from=0, to=0.5, by=0.0001)
y_none_to_mild_bleaching=dgamma(x_testing,as.numeric(turbidity_distribution_none_to_mild_bleaching$estimate['shape']),as.numeric(turbidity_distribution_none_to_mild_bleaching$estimate['rate']))
y_moderate_to_severe_bleaching=dgamma(x_testing,as.numeric(turbidity_distribution_moderate_to_severe_bleaching$estimate['shape']),as.numeric(turbidity_distribution_moderate_to_severe_bleaching$estimate['rate']))

x_testing[y_none_to_mild_bleaching>y_moderate_to_severe_bleaching]
#0.0803 is when none_to_mild_bleaching has a greater probability density than moderate_to_severe_bleaching
```