---
title: "Great_Barrier_Reef_turbidity_gradient"
author: "SS"
date: "November 23, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#This is a case study of a turbidty gradient in the Great Barrier Reef. We read in a csv that contains the lat/lon coordinates of reefs along this turbidity gradient and contains the reef flat size. We extract the corresponding Kd490 values from the mean_turbidity_globally raster. We perform a non-linear least squares regression.

```{r load libraries}
library(raster)
library(rddtools)
library(nls2)
library(VGAM)
library(investr)
library(grDevices)
library(viridis)
```

home<-"C:/Users/Shannon/Desktop/Ecoregions/turbidity/Final"
setwd(home)
Australia_reefs <- read.csv(file=file.path(home,"Australia_Islands_Reef_Measurements.csv"), header=TRUE, sep=",")
names(Australia_reefs)[names(Australia_reefs)=="ï..Islands"]<-"Islands"

```{r obtain turbidity values for each Australia reef and write a new csv}
Australia_points<-cbind(Australia_reefs$Long_Deg, Australia_reefs$Lat_Deg)
turbidity_raster<-raster("turbidity_raster_mean.nc")
result <- extract(turbidity_raster, Australia_points)
Australia_reefs$turbidity<-result

write.csv(Australia_reefs, file=file.path(home,'Australia_Turbidity_Final.csv'),row.names=T)
```

```{r nonlinear model and plot}
y=Australia_reefs$Average_Distance
x=Australia_reefs$turbidity
m <- nls(y ~ a*exp(-b*x), start=list(a=1500, b=10), control=nls.control(maxiter=10000, minFactor=1e-7, tol=1e-5, printEval=F, warnOnly=F))
summary(m)
coeff_a=round(summary(m)$coefficients[1,1],2)
coeff_b=round(summary(m)$coefficients[2,1],2)

png(file=file.path(home,'FigureS4.png'),height=1200,width=2600,res=300)
plot(x,y, ylim=c(0,1600), xlim=c(0.05,.165), ylab="Width of reef flat (m)", xlab=expression("K"[d]*"490"), bg="black", col="black", pch=21)
newdataframe<-as.data.frame(cbind(x=Australia_reefs$turbidity, y=Australia_reefs$Average_Distance))
newdataframe<-newdataframe[!is.na(newdataframe$x),]
newdataframe<-newdataframe[with(newdataframe, order(x)), ]
confidence_intervals<-predFit(m, level=0.95, newdata=newdataframe, interval="confidence")
polygon(x=c(newdataframe$x[1],newdataframe$x,newdataframe$x[length(newdataframe$x)]), y=c(0,confidence_intervals[,3],0), col=adjustcolor("gray", alpha=.5), border=NA)
polygon(x=c(newdataframe$x[1],newdataframe$x,newdataframe$x[length(newdataframe$x)]), y=c(0,confidence_intervals[,2],0), col="white", border=NA)
c=seq(0.049,.165, .001)
lines(c,coeff_a*exp(-1*coeff_b*c), lwd=2.5, col="black", xlim=c(0.05,.165))
points(x,y, ylim=c(0,1600), xlim=c(0.05,.146), bg="black", col="black", pch=21)
dev.off()
confint(m, parm=c('a','b'), level = 0.95)
```

```{r examine where the 95% confidence interval crosses zero}
cross_zero<-predFit(m, level=0.95, newdata=data.frame(x=seq(from=.1264, to=.1266, by=.0001)), interval="confidence")
#the lower 95% confidence interval crosses zero at ~0.127
```
